Modern Graph Generators: A Survey

### 2018-10-08 comparison.tex
More precise information about operations

\begin{tabular}{| c | p{3.3cm} | p{2cm} |  p{2cm} | p{1.3cm} |  l | l | p{3.2cm} | p{2cm} | l | }

@@

 & \cite{Duan:2011:AOC:1989323.1989340} & extracted & -- & N & Y &N & -- &  RDF & N    \\

@@

 & LinkGen & schema-driven & user-defined & templates & Y  & N & Gaussian, Zipfian & RDF & N\\

@@

  & XGDBench & fixed  & social network  & fixed & Y & Y & power-law &  MAG &  Y  \\

@@

 & LinkBench & fixed & social network & Y & Y & Y & Facebook & impl. NA & -- \\

@@

 & LDBC SNB  & fixed & social network &  generated & Y  & Y & Facebook &  CSV, RDF & Y     \\

@@

  & HPC Scal. Graph Anal. & fixed & -- & Y & N& N& uniform &edge-list & N   \\

@@

  & Graphalytics & extracted & social network & Y& N& N & power-law & CSV, RDF & N   \\

>>>>

\begin{tabular}{| c | p{3cm} | p{2cm} |  p{2cm} | p{1.3cm} |  l | l | p{3.2cm} | p{2cm} | l | }

@@

 & \cite{Duan:2011:AOC:1989323.1989340} & extracted & -- & N & N & Y & -- &  RDF & N    \\

@@

 & LinkGen & schema-driven & user-defined & templates & N  & N & Gaussian, Zipfian & RDF & N\\

@@

  & XGDBench & fixed  & social network  & generated & generated & Y & power-law &  MAG &  Y  \\

@@

 & LinkBench & fixed & social network & generated & generated & Y & Facebook & impl. NA & -- \\

@@

 & LDBC SNB  & fixed & social network &  generated & generated  & Y & Facebook &  CSV, RDF & Y     \\

@@

  & HPC Scal. Graph Anal. & fixed & -- & fixed & N& N& uniform &edge-list & N   \\

@@

  & Graphalytics & extracted & social network & fixed& N& N & power-law & CSV, RDF & N   \\
